Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
adds rest of Mehrdad's text.

In reality, not all released electrons may be able to proceed the next ionization.
If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3 \\
  \label{eq:N_i1} & = & 1 + \xi + 2 \xi^2 + 4 \xi ^3 \, .
\end{eqnarray}
%%%%%%%%%
Alternatively, cascade (\emph{ii}) leads to
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & \frac{1 - \xi^k}{1 - \xi} \\
  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
\end{eqnarray}
%%%%%%%%%
where $k \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
In Appendix \ref{sec:AppendixB}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) is probably more realistic.

@@

\section{Ionization Cascade}
\label{sec:AppendixB}

For an electron-hydrogen ionizing collision, we estimate the differential cross section $\sigma$ as a function of recoil energy $d\sigma / dE_{\rm recoil}$.
We approximate the bound electron as a free one at rest and use the differential cross section for scattering of two electrons (Bhabha scattering) in the non-relativistic limit:
\begin{equation}
\label{eq:dsig/dOmeg} \frac{d\sigma}{d\Omega_{\rm CM}} \sim \frac{\alpha^2}{m_e^2 v_{\rm rel}^2 \sin^4 \theta} \, ,
\end{equation}
where $\alpha$ is the fine structure constant, $v_{\rm rel}$ is the relative velocity, $\theta$ is the scattering angle in the center of mass (CM) frame, and $m_e$ is the electron mass.
The recoil energy (that is, the energy transferred to the electron at rest) is related to the scattering angle via
\begin{equation}
  \label{eq:Erec} = \frac{1}{4} m_e v_{\rm rel}^2 \left( 1 - \cos \theta \right) \, ,
\end{equation}
and hence
\begin{equation}
  \label{eq:dErec/dOmeg} \frac{dE_{\rm recoil}}{d\Omega_{\rm CM}} = -\frac{1}{4} m_e v_{\rm rel}^2 \, .
\end{equation}
We therefore have
\begin{equation}
  \label{eq:dsig/dErec} \frac{d\sigma}{dE_{\rm recoil}} \sim \frac{\alpha^2}{m_e v_{\rm rel}^2 E_{\rm recoil}^2} \, ,
\end{equation}
which is largest for small recoil energies.
Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful. 
%This suggests that if the energetic electron ends up ionizing other atoms, it is more likely to put them right at the threshold of

\section{Comparison with previous work}
\label{sec:AppendixA}

>>>>

In reality, not all released electrons may be able to proceed the next ionization.
If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3 \\
  \label{eq:N_i1} & = & 1 + \xi + 2 \xi^2 + 4 \xi ^3 \, .
\end{eqnarray}
%%%%%%%%%
Alternatively, cascade (\emph{ii}) leads to
%%%%%%%%%
\begin{eqnarray}
  \nonumber N_i & = & \frac{1 - \xi^k}{1 - \xi} \\
  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
\end{eqnarray}
%%%%%%%%%
where $k \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
In Appendix \ref{sec:AppendixA}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) -- unequal recoil energies -- is probably more realistic.

@@

\section{Ionization Cascade}
\label{sec:AppendixA}

For an electron-hydrogen ionizing collision, we estimate the differential cross section $\sigma$ as a function of recoil energy $d\sigma / dE_{\rm recoil}$.
We approximate the bound electron as a free one at rest and use the differential cross section for scattering of two electrons (Bhabha scattering) in the non-relativistic limit:
\begin{equation}
\label{eq:dsig/dOmeg} \frac{d\sigma}{d\Omega_{\rm CM}} \sim \frac{\alpha^2}{m_e^2 v_{\rm rel}^2 \sin^4 \theta} \, ,
\end{equation}
where $\alpha$ is the fine structure constant, $v_{\rm rel}$ is the relative velocity, $\theta$ is the scattering angle in the center of mass (CM) frame, and $m_e$ is the electron mass.
The recoil energy (that is, the energy transferred to the electron at rest) is related to the scattering angle via
\begin{equation}
  \label{eq:Erec} = \frac{1}{4} m_e v_{\rm rel}^2 \left( 1 - \cos \theta \right) \, ,
\end{equation}
and hence
\begin{equation}
  \label{eq:dErec/dOmeg} \frac{dE_{\rm recoil}}{d\Omega_{\rm CM}} = -\frac{1}{4} m_e v_{\rm rel}^2 \, .
\end{equation}
We therefore have
\begin{equation}
  \label{eq:dsig/dErec} \frac{d\sigma}{dE_{\rm recoil}} \sim \frac{\alpha^2}{m_e v_{\rm rel}^2 E_{\rm recoil}^2} \, ,
\end{equation}
which is largest for small recoil energies.
Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful.

An objection to the above estimate is that the singularity in the $E_{\rm recoil} \rightarrow 0$ limit arises from the long range nature of Coulomb interaction which of course is absent in the real problem.
Far away, the ionizing electron sees the dipole moment of the neutral atom.
However, for energy transfer of order a Rydberg $\alpha/2a_0$ we can estimate the transfer momentum and see that it is larger than the inverse of the Bohr radius $a_0$.
This implies that in this range the above estimate may actually be reliable. The transfer momentum is
\begin{equation}
q^2 =\frac{1}{4} m^2 \vrel^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2\vrel^2 \sin^2 \frac{\theta}{2}.
\end{equation}
Comparison with (\ref{eq:Erec}) shows
\begin{equation}
E_{\rm recoil} = \frac{q^2}{2m}.
\ee
Now set $E_{\rm recoil} \sim \alpha/a_0$ to get
\be
q \sim \sqrt{\frac{m\alpha}{a_0}}\sim \frac{1}{a_0}
\ee
where we used $a_0 = 1/\alpha m$.

\section{Comparison with previous work}
\label{sec:AppendixB}
